\begin{lemma}
Let \(s,n\ge 3\), and suppose \(F\) and \(G\) are \((n,d(F),\lambda(F))\)- and \((n,d(G),\lambda(G))\)-graphs on the same vertex set, with \(d(F),d(G)>0\). If \((F,G)\) is \(H_s\)-free, set
\[
  \eta=\max\left\{\frac{\lambda(G)^2}{d(G)^2},
  \frac{\lambda(F)\lambda(G)}{d(F)d(G)}\right\},
  \qquad
  w=\frac{4n\log n}{d(G)}.
\]
Assume also that \(0\le \eta\le 1\).
Then there is a \(T_s\)-free digraph \(D\) on \(d(F)n\) vertices such that, for all \(k\ge w\),
\[
  \overrightarrow{i_k}(D)\le 16^k \eta^{k-w}(d(F)n)^k.
\]
\end{lemma}
\begin{proof}
Let \(W\) be the product vertex set from \(\noderef{ProductDigraphVertex}\), namely
\[
  W=\{(a,b): a,b\in V,\ ab\in E(F)\},
\]
and let \(D=D(F,G)\) be the product digraph on \(W\) defined in \(\noderef{ProductDigraph}\). By \(\noderef{ProductDigraph}\), an arc
\[
  (a_1,b_1)\to(a_2,b_2)
\]
in \(D\) is exactly the assertion \(a_1b_2\in E(G)\).

We first record the two structural properties of \(D\). Since \(F\) is an \((n,d(F),\lambda(F))\)-graph, \(\noderef{LoopGraphNdLambda}\) gives \(|V|=n\), and \(\noderef{LoopGraphDegree}\) gives exactly \(d(F)\) choices of \(b\) with \(ab\in E(F)\) for each fixed \(a\in V\). Therefore
\[
  |W|=d(F)n.
\]
Also, \(\noderef{ProductDigraphTransitiveFree}\), applied to the hypothesis that \((F,G)\) is \(H_s\)-free, gives that \(D\) is \(T_s\)-free.

It remains to bound the number of forward independent tuples. Fix \(k\ge w\), and let
\[
  \mathbf v=(v_1,\ldots,v_k)
\]
be a forward independent \(k\)-tuple in \(D\). Write \(v_i=(a_i,b_i)\). By \(\noderef{ProductDigraphTupleHasShrinkingSequence}\), the tuple \(\mathbf v\) has a unique binary shrinking sequence
\[
  z^{\mathbf v}\in\{0,1\}^k,
\]
where a true bit is exactly the large-neighborhood case
\[
  |N_G(a_i)\cap B_i|>\frac{d(G)|B_i|}{2n},
  \qquad
  B_i=V\setminus\bigcup_{j<i}N_G(a_j).
\]
The same definition includes the forward-independence condition, so every tuple counted by \(\noderef{ForwardIndependentTupleCount}\) is counted by exactly one fixed-sequence class from \(\noderef{ProductDigraphFixedSequenceTupleCount}\).

We next prove that the weight of \(z^{\mathbf v}\) is at most \(w\). By \(\noderef{BinarySequenceWeight}\), this weight is the number of true, or large-neighborhood, indices. For every \(i\), the vertex \(b_i\) belongs to \(B_i\): if \(j<i\), then \(\noderef{ForwardIndependentTuple}\) applied to the forward independent tuple \(\mathbf v\) says that there is no arc \(v_j\to v_i\), and the arc definition in \(\noderef{ProductDigraph}\) therefore implies \(a_jb_i\notin E(G)\). Hence \(B_i\) is nonempty for every \(i\). When \(z^{\mathbf v}_i=1\), the large-neighborhood inequality gives
\[
  |N_G(a_i)\cap B_i|>\frac{d(G)}{2n}|B_i|.
\]
Since
\[
  B_{i+1}=B_i\setminus N_G(a_i),
\]
we get
\[
  |B_{i+1}|<\left(1-\frac{d(G)}{2n}\right)|B_i|
\]
at every true bit. The graph \(G\) has degree \(d(G)\) on an \(n\)-vertex set by \(\noderef{LoopGraphNdLambda}\) and \(\noderef{LoopGraphDegree}\), so \(0<d(G)\le n\). Thus \(0<d(G)/(2n)\le1/2\), and repeated application of the preceding inequality shows that after \(r\) true bits,
\[
  |B_i|\le n\left(1-\frac{d(G)}{2n}\right)^r
  \le n\exp\left(-\frac{r\,d(G)}{2n}\right).
\]
Suppose, for contradiction, that the tuple has \(r>w\) true bits in total. Among the first \(k-1\) positions there are at least \(r-1>w-1\) true bits, so the preceding estimate applied to \(B_k\) gives
\[
  |B_k|
  < n\exp\left(-\frac{(w-1)d(G)}{2n}\right).
\]
Using \(w=4n\log n/d(G)\), this upper bound is
\[
  n\exp\left(-2\log n+\frac{d(G)}{2n}\right)
  \le n\exp(-2\log n+1/2)
  =\frac{\sqrt e}{n}<1,
\]
because \(d(G)\le n\) and \(n\ge3\). This contradicts \(b_k\in B_k\), proved above. Therefore every forward independent \(k\)-tuple has shrinking-sequence weight at most \(w\).

We can now partition the forward independent \(k\)-tuples according to their shrinking sequence. The preceding paragraph shows that only binary sequences \(z\in\{0,1\}^k\) with \(|z|\le w\) occur, so by \(\noderef{ForwardIndependentTupleCount}\), \(\noderef{ProductDigraphTupleHasShrinkingSequence}\), and \(\noderef{ProductDigraphFixedSequenceTupleCount}\),
\[
  \overrightarrow{i_k}(D)
  \le \sum_{\substack{z\in\{0,1\}^k\\ |z|\le w}}
      C(k,z),
\]
where \(C(k,z)\) denotes the fixed-sequence tuple count. For each such \(z\), \(\noderef{ProductDigraphShrinkingSequenceBound}\) applies, using \(n>0\), \(d(F)>0\), and \(d(G)>0\), and gives
\[
  C(k,z)\le (8\eta)^{k-|z|}(d(F)n)^k.
\]

Finally we estimate the sum. Since \(0\le\eta\le1\), \(k\ge w\), and \(|z|\le w\), we have
\[
  \eta^{k-|z|}\le \eta^{k-w}.
\]
Also \(8^{k-|z|}\le 8^k\). Hence
\[
  (8\eta)^{k-|z|}(d(F)n)^k
  \le 8^k\eta^{k-w}(d(F)n)^k
\]
for every occurring \(z\). There are at most \(2^k\) binary sequences of length \(k\), so
\[
  \overrightarrow{i_k}(D)
  \le 2^k\cdot 8^k\eta^{k-w}(d(F)n)^k
  =16^k\eta^{k-w}(d(F)n)^k.
\]
This proves the required bound for the fixed \(k\), and since \(k\ge w\) was arbitrary, the lemma follows.
\end{proof}
